% YAAC Another Awesome CV LaTeX Template
%
% This template has been downloaded from:
% https://github.com/darwiin/yaac-another-awesome-cv
%
% Author:
% Christophe Roger
%
% Template license:
% CC BY-SA 4.0 (https://creativecommons.org/licenses/by-sa/4.0/)
%Section: Work Experience at the top
\sectionTitle{Experience}{\faSuitcase}
%\renewcommand{\labelitemi}{$\bullet$}
\begin{experiences}
  \experience
  {Present}  {Master Software Engineer At The Manager Level}{Capital One Finance}
  {October 2021}   {
                      \begin{itemize}
                        \item Tech Lead for team responsible for building financial products.
                        \item Worked with leaders from Lola and Captial One to transition the Lola team and to shut down parts of Lola's operation. 
                      \end{itemize}
                  }
                  {Python, Flask, PostgreSQL, AWS}
  \emptySeparator
  \experience
  {October 2021}  {Engineering Manager}{Lola.com {\footnotesize (Acquired by Captial One Finance in October 2021)}}
  {May 2019}   {
                      \begin{itemize}
                        \item Lead the team responsible for strengthening Lola's support tooling infrastructure. Established an agile workflow and worked with the team to build front and backend systems to surface critical information to agents as soon as it was needed.
                        \item Moved over to lead the team responsible for the core corporate spend/budgeting product. Building out functionality while managing the teams workflow and ensuring continued growth.
                        \item Established a system for individual contributors across teams to discuss architectural issues and lobby management to level up Lola's Technical infrastructure. 
                        \item Championed, managed, and participated in the project to port legacy systems to Python 3 ensuring the future maintainability and health of the entire system.
                      \end{itemize}
                  }
                  {Python, Javascript, Starlette, Flask, SQLAlchemy, PostgreSQL, Redis, Graphql, React, AWS, Kubernetes}
  \emptySeparator
  \experience
  {May 2019}  {Lead Software Engineer}{Fitbit {\footnotesize (September 2018 - May 2019)}}
  {January 2016}   {
                      \begin{itemize}
                        \item Lead his team’s effort to transition several services from Softlayer into Google Compute Engine. Documenting and spreading the knowledge gained to enable teams following them to handle their move more efficiently.
                        \item Designed and built tooling to analyze device battery life, prevent warranty fraud, and improved customer support by building visibility into products.
                      \end{itemize}
                  }
                  {}
  \experience
  {}  {Senior Software Engineer}{Fitbit {\footnotesize (March 2017 - September 2018)}}
  {}   {
                      \begin{itemize}
                        \item Assisted platform teams in refactoring central domain models to enable the transition from a monolithic system to microservices.
                        \item Managed one of the cross team, multi national, cross functional projects to ensure Fitbit’s compliance to the EU’s GDPR law.
                      \end{itemize}
                  }
                  {}
   \experience
  {}  {Software Engineer}{Fitbit {\footnotesize (January 2016 - March 2017)}}
  {}   {
                      \begin{itemize}
                        \item Spearheaded the commerce platform SOX compliance efforts. Worked with auditors and stakeholders to ensure engineering provided appropriate audits and controls. This included a complete revamp of deployment pipeline and the authentication mechanisms of the commerce backend.
                        \item Built full stack functionality to support product sales on the Fitbit.com commerce platform. Including but not limited to: product warranties, chargeback fraud prevention, and product launch support.
                      \end{itemize}
                  }
                  {Java, Python, Spring, Ansible, Mysql, Cassandra, Zookeeper, Prometheus, Kibana, Grafana, Kafka, Finagle, Thrift, Google Compute Engine, JavaScript, Ember.js, JSP, Jenkins}
\emptySeparator
  \experience
  {December 2015}  {Software Engineer}{Cloudlock}
  {October 2012}   {
                      \begin{itemize}
                        \item Developed compliance and DLP applications on Google's App Engine and Amazon's AWS cloud platforms.
                        \item Built an internal service that scans millions of items per day for PCI, PII, Login Credentials and other information companies want to track in their various cloud environments.
                        \item Developed features around several of Google's APIs including Drive, the Admin SDK, Google+ and others.
                      \end{itemize}
                  }
                  {Python, Google App Engine, AngularJS, Java, pytest, PDFBox, Apache POI, Librato, Flask, Django, Postgres, Jinja, Jenkins}
\emptySeparator
  \experience
  {September 2012}  {Software Engineer}{CrunchTime! Information Systems}
  {June 2011}   {
                      \begin{itemize}
                        \item Developed and maintained a web application to assist restaurant managers in cutting costs by managing labor and inventory.
                        \item Implemented several reports pages and ported legacy Perl code to modern Java.   
                        \item Assisted in transitioning from an Ant based build to a Maven build.
                      \end{itemize}
                  }
                  {Java, Perl, Spring, JavaScript, jQuery, MyBatis, Oracle Database, JSP}
\end{experiences}
